### 2017-02-20 paper/paper.tex
fixed \mathcal

\begin{table}[h]
\begin{center}
\begin{tabular}{r | c c c}
& Skew & SA-IS & \textbf{GSACA} \\
\hline
Art & \textcolor{rot}{rekursiv} & \textcolor{rot}{rekursiv} & \textcolor{gruen}{iterativ} \\
Zeit & $\mathcol{O}(n)$ & $\mathcol{O}(n)$ & $\mathcol{O}(n)$ \\
Speicher & $\mathcol{O}(\log n) + \max 24n$ & $\mathcol{O}(\log n) + \max 2n$ & $\mathcol{O}(1)\ +\ ?$
\end{tabular}

>>>>

\begin{table}[h]
\begin{center}
\begin{tabular}{r | c c c}
& Skew & SA-IS & \textbf{GSACA} \\
\hline
Art & \textcolor{rot}{rekursiv} & \textcolor{rot}{rekursiv} & \textcolor{gruen}{iterativ} \\
Zeit & $\mathcal{O}(n)$ & $\mathcal{O}(n)$ & $\mathcal{O}(n)$ \\
Speicher & $\mathcal{O}(\log n) + \max 24n$ & $\mathcal{O}(\log n) + \max 2n$ & $\mathcal{O}(1)\ +\ ?$
\end{tabular}
